Figures to insert in text

### 2018-04-10 Chapters/Chapter01.tex

The transactions are classified into three groups: (i) confirmed transactions, (ii) confirming transactions, and (iii) unconfirmed transactions (tips). The confirmed transaction are the ones which have already been settled, i.e., their accumulated weights have reached a minimum level. The unconfirmed transactions (tips) are the very new transactions which have not been confirmed even once yet, i.e., their accumulated weights are zero. The confirming transactions are in the middle. They have already been confirmed a few times, but not enough to reach the minimum level required to be a confirmed transaction.

A ``block'' is just a regular transaction with no inputs which confirms a previous block and at least two confirming transactions or tips. There may be any number of outputs provided that they comply with the number of newly generated tokens. Each block collects all fees from all transactions confirmed by it which have not been confirmed by another block before.

@@

The incentive schema which keeps the network running is the same as Bitcoin's. Miners go towards fees and newly generate coins, while users go towards exchanging their tokens.

Let $A$ be a transaction, $w_A$ be its weight, and $\text{acc}_A$ be its accumulated weight. Then, $\text{acc}_A = w_A + \sum_{A \leadsto P} w_P$.

>>>>

The transactions are classified into three groups: (i) confirmed transactions, (ii) in-progress transactions, and (iii) unconfirmed transactions (tips). The confirmed transaction are the ones which have already been settled, i.e., their accumulated weights have reached a minimum level. The unconfirmed transactions (tips) are the brand new transactions which have not been confirmed even once yet, i.e., their accumulated weights are zero. The in-progress transactions are in the middle. They have already been confirmed a few times, but not enough to reach the minimum level required to be a confirmed transaction.

A ``block'' is just a regular transaction with no inputs which confirms a previous block and at least two in-progress transactions or tips. There may be any number of outputs provided that they comply with the number of newly generated tokens. Each block collects all fees from all transactions confirmed by it which have not been confirmed by another block before.

@@

The incentive scheme which keeps the network running is the same as Bitcoin's. Miners go towards fees and newly generate coins, while users go towards exchanging their tokens.

The concepts of weight and accumulated weight are the same as Iota's, but their equations are different. The weight of a transaction is calculated as $\log_2(k)$ where $k$ is the average number of hashes required to solve its proof-of-work again, while the accumulated weighted of a transaction A with weight $w_A$ is calculated as $\log_2(2^{w_A} + \sum_{A \leadsto P} 2^{w_P})$. The $\log$ function is used to reduce the magnitude of the numbers. Hence, the power-of-2 of the accumulated weight is a measure of the average number of hashes required to solve the proof-of-work of all transactions that are confirming A.

In Bitcoin, it is usually required 6 confirmations before accepting a transaction. Let $H$ be the total hash rate of the network. Then, as $\mathbf{E}(Y_6) = 60 \text{ minutes}$, it will be necessary to calculate, on average, $\mathbf{E}(Y_6) \cdot H = 60 \cdot 60 \cdot H$ hashes to solve the proof-of-work of 6 blocks. Finally, a transaction is said to be confirmed when its accumulated weight is greater than or equal to $\log_2(\mathbf{E}(Y_6) \cdot H) = \log_2(60 \cdot 60 \cdot H) = \log_2(3600) + \log_2(H) = 4 + \log_2(225) + \log_2(H)$, where $H$ is calculated as the total hash rate of the miners plus the total hash rate of new transactions.
